% Experience section
\vspace{-0.65cm}
\section{Professional Experience}
\resumeSubHeadingListStart
    \vspace{-0.25cm}
    \resumeExperienceEntry{Machine Learning Engineer}{Google}{Mountain View, CA}{Jan 2021 - Present}
    \resumeItemListStart
        \resumeItem{Designed and implemented machine learning models for predictive analytics and recommendation systems.}
        \resumeItem{Collaborated with data scientists and software engineers to deploy models in production using Docker and Kubernetes.}
        \resumeItem{Optimized model performance and scalability, reducing inference time by 30\%.}
        \resumeItem{Conducted A/B testing and model validation to ensure accuracy and reliability.}
    \resumeItemListEnd

    \resumeExperienceEntry{Data Scientist}{Facebook}{Menlo Park, CA}{Jun 2018 - Dec 2020}
    \resumeItemListStart
        \resumeItem{Developed data pipelines and ETL processes to clean and preprocess large datasets.}
        \resumeItem{Built machine learning models for customer segmentation and churn prediction using Python and scikit-learn.}
        \resumeItem{Visualized data insights using Matplotlib and Seaborn to support business decision-making.}
        \resumeItem{Collaborated with cross-functional teams to integrate data-driven solutions into business processes.}
    \resumeItemListEnd

    \resumeExperienceEntry{Research Assistant}{MIT}{Cambridge, MA}{Sep 2016 - May 2018}
    \resumeItemListStart
        \resumeItem{Conducted research on deep learning algorithms for image and speech recognition.}
        \resumeItem{Published research papers in top-tier conferences and journals.}
        \resumeItem{Assisted in teaching machine learning courses and mentoring undergraduate students.}
    \resumeItemListEnd

    \resumeExperienceEntry{Research Assistant}{Example University}{Anytown, USA}{Jan 2024 - Jun 2024}
    \resumeItemListStart
        \resumeItem{Created an end-to-end autonomous driving system leveraging Python, benchmarking simulation versus real-world performance while optimizing diverse navigation strategies (local, hybrid, and cloud).}
        \resumeItem{Engineered a custom communication protocol and a scalable deployment framework supporting multi-user access.}
        \resumeItem{Led comprehensive model evaluations to boost system reliability by 15\% and increasing battery backup per charge by 12\%.}
        \resumeItem{Leveraged strong skills in PyTorch and Linux to execute, train, and deploy multiple models, showcasing expertise in communication networks and scalable system design.}
    \resumeItemListEnd

    \resumeExperienceEntry{Teaching Assistant}{Example University}{Anytown, USA}{Sep 2024 - Dec 2024}
    \resumeItemListStart
        \resumeItem{Served as Teaching Assistant for Example Course, collaborating with professor to design assignments focused on robot navigation and policy learning while addressing complex robotics concepts.}
        \resumeItem{Provided tailored support during office hours and provided detailed feedback on student projects—including autonomous robot and simulation environments—enhancing student comprehension and engagement.}
    \resumeItemListEnd

    \resumeExperienceEntry{Graduate Intern}{Example University}{Anytown, USA}{Jan 2024 - Jun 2024}
    \resumeItemListStart
        \resumeItem{Aided with Career Development Officer to manage student alumni program, analyzing data, and identifying key engagement trends.}
        \resumeItem{Analyzed 200+ alumni records using Excel techniques, generating insights that improved program oversight and strategic initiatives.}
        \resumeItem{Developed robust skills in data analytics, program management, catalyzing more effective monitoring and continuous improvement of alumni engagement strategies.}
    \resumeItemListEnd

    \resumeExperienceEntry{Process Optimization Intern}{Example Company}{Anytown, USA}{Sep 2019 - Mar 2021}
    \resumeItemListStart
        \resumeItem{Led mechanical engineering and simulation efforts within Example Company for national level competition, targeting improved process optimization and performance validation through advanced simulation techniques in robotics.}
        \resumeItem{Drove a 25\% reduction in development cycle time, a 15\% increase in overall project efficiency, and a 10\% reduction in operational costs; additionally, devised MATLAB simulations using Simulink and Simscape that contributed to winning an award.}
        \resumeItem{Constructed expertise in mechanical design, process optimization, and advanced simulation using MATLAB, skills that facilitate to provide effective solutions in robotics and engineering projects.}
    \resumeItemListEnd

    \resumeExperienceEntry{Senior Software Engineer}{ABC Corp}{Anytown, USA}{Jan 2020 - Present}
    \resumeItemListStart
        \resumeItem{Developed and maintained web applications using JavaScript, React, and Node.js.}
        \resumeItem{Collaborated with product managers and designers to create user-friendly interfaces.}
        \resumeItem{Mentored junior developers and conducted code reviews.}
    \resumeItemListEnd

    \resumeExperienceEntry{Software Engineer}{XYZ Inc}{Anytown, USA}{Jun 2017 - Dec 2019}
    \resumeItemListStart
        \resumeItem{Worked on a team to develop a large-scale e-commerce platform.}
        \resumeItem{Implemented RESTful APIs and integrated third-party services.}
        \resumeItem{Optimized application performance and improved user experience.}
    \resumeItemListEnd

\resumeSubHeadingListEnd