% Projects section
\vspace{-0.65cm}
\section{Relevant Academic Projects}
\resumeSubHeadingListStart
    \vspace{-0.25cm}
    \resumeProjectEntry{Deep Learning for Image Classification at Google}{Jan 2022 - Mar 2022}
    \resumeItemListStart
        \resumeItem{Developed a convolutional neural network (CNN) using TensorFlow to classify images from the CIFAR-10 dataset.}
        \resumeItem{Achieved an accuracy of 98\% on the test set by implementing data augmentation and hyperparameter tuning.}
        \resumeItem{Deployed the model using Flask and Docker for real-time image classification.}
    \resumeItemListEnd
      
    \resumeProjectEntry{Natural Language Processing for Sentiment Analysis at Facebook}{Apr 2022 - Jun 2022}
    \resumeItemListStart
        \resumeItem{Built a sentiment analysis model using LSTM networks in Keras to classify social media posts as positive or negative.}
        \resumeItem{Preprocessed text data using tokenization, stemming, and lemmatization techniques.}
        \resumeItem{Achieved an F1-score of 0.95 on the validation set.}
    \resumeItemListEnd
      
    \resumeProjectEntry{Reinforcement Learning for Game AI at OpenAI}{Jul 2022 - Sep 2022}
    \resumeItemListStart
        \resumeItem{Implemented a reinforcement learning agent using Q-learning to play the game of Snake.}
        \resumeItem{Optimized the agent's performance using deep Q-networks (DQN) and experience replay.}
        \resumeItem{Achieved a high score of 250 in the game environment.}
    \resumeItemListEnd
      
    \resumeProjectEntry{Predictive Modeling for Financial Forecasting at Goldman Sachs}{Oct 2022 - Dec 2022}
    \resumeItemListStart
        \resumeItem{Developed a predictive model using XGBoost to forecast stock prices based on historical data.}
        \resumeItem{Performed feature engineering and selection to improve model accuracy.}
        \resumeItem{Achieved a mean absolute percentage error (MAPE) of 2.5\%.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
